\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Roman Suleimanov} \\ \vspace{1pt}
    \small +7 (981) 939-87-39 $|$ \href{mailto:jojou112@gmail.com}{\underline{jojou112@gmail.com}} $|$
    \href{https://t.me/jojouHZ}{\underline{t.me/jojouHZ}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rostov Trade and Economic College}{Rostov-on-Don, Russia}
      {Diploma in Software for Computer Systems and Automated Systems}{2002 -- 2006}
    \resumeSubheading
      {Taganrog State University of Radio Engineering (TRTU)}{Taganrog, Russia}
      {Bachelor's Degree in Automation of Technological Processes and Production, Digital Control of Production Complexes}{2006 -- 2010}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Offset Printer}{2010 -- Mar 2018}
      {Various Printing Houses}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Operated and maintained offset printing machines to produce high-quality printed materials.}
        \resumeItem{Monitored print quality, adjusting color balance, registration, and ink density as needed.}
        \resumeItem{Prepared and calibrated printing plates, ensuring accurate image and text reproduction.}
      \resumeItemListEnd
    \resumeSubheading
      {Internet Projects Manager}{Mar 2018 -- Jul 2023}
      {Alidi}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Managed the creation and operation of official online stores on marketplaces (AliExpress, Alibaba, Amazon, Yandex Market, Goods.ru) for brands such as P\&G, Gillette, Coca-Cola, Mars, and Nestlé.}
        \resumeItem{Developed scripts to automate warehouse processes, improving order fulfillment and shipping efficiency.}
        \resumeItem{Collaborated with brand representatives to resolve claim situations and ensure smooth operations.}
      \resumeItemListEnd
    \resumeSubheading
      {Game Developer}{Oct 2023 -- Oct 2024}
      {\href{https://store.steampowered.com/app/3687350/Tiny_Truck_Simulator/}{Tiny Truck Simulator (Indie Project)}}{Remote}
      \resumeItemListStart
        \resumeItem{Developed core game mechanics, including vehicle physics and controls.}
        \resumeItem{Implemented gameplay features using C++ and Unreal Engine Blueprints.}
      \resumeItemListEnd
    \resumeSubheading
      {Administrator / Webmaster}{Jun 2024 -- Jun 2025}
      {Shrinadji Academy}{Tbilisi, Georgia}
      \resumeItemListStart
        \resumeItem{Maintained and updated the academy's website, ensuring smooth operation and user accessibility.}
        \resumeItem{Organized and managed live streaming events, ensuring high-quality broadcasts and technical support.}
        \resumeItem{Provided user support, resolving technical issues and improving user experience.}
        \resumeItem{Automated internal workflows using low-code/no-code tools and custom JavaScript/Python scripting.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://store.steampowered.com/app/3687350/Tiny_Truck_Simulator/}{Tiny Truck Simulator}} $|$ \emph{C++, Unreal Engine, Blueprints}}{Oct 2023 -- Oct 2024}
      \resumeItemListStart
        \resumeItem{Developed core game mechanics, including vehicle physics and controls.}
        \resumeItem{Implemented gameplay features using C++ and Unreal Engine Blueprints.}
        \resumeItem{Published the game on \href{https://store.steampowered.com/app/3687350/Tiny_Truck_Simulator/}{Steam}.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Code Diff Viewer} $|$ \emph{TypeScript, React, Monaco Editor, IndexedDB, rc-slider, react-diff-view}}{Recent}
      \resumeItemListStart
        \resumeItem{Developed an interactive code difference viewer with real-time comparison.}
        \resumeItem{Implemented Monaco Editor for code editing and visualization.}
        \resumeItem{Used IndexedDB for client-side data storage and management.}
        \resumeItem{Integrated rc-slider and react-diff-view for enhanced user interaction.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Python, JavaScript, TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Unreal Engine} \\
     \textbf{Tools}{: Git, VS Code, Webpack, ESLint, Prettier, Monaco Editor, IndexedDB} \\
     \textbf{Technologies}{: REST API, WebSockets, Docker (basic knowledge), CI/CD (GitHub Actions)}
    }}
 \end{itemize}

\end{document}
